### 2014-10-16 fundamentals/intro.tex
spellcheck

Historically, nuclear fuel cycle simulators have estimated 
nuclear fuel cycle performance using software 
ranging from ad hoc spreadsheet-driven flow calculators to highly specialized 
proprietary models. To date, current tools are either static, fleet-based, 
privately distributed, or all of the above. Each of these qualities present a 
severe challenge to modeling fidelity, generality, effciiency, robustness, and 
scientific transparency.

@@

% Common goals of fuel cycle simulation/simulators (driving r&d focus,
% approximating tech. impacts, etc.)
% Previous work (cite all the tools!)
% Limitations of previous simulators by others (fleet-based, closed
% development, inflexible infrastructure)
% Previous attempts by this group (GENIUS v1/v2)
% note NGFCS

@@

This cycle has resulted in a a proliferation of specialized
fuel cycle simulators for the calculation of fuel cycle metrics.  Accordingly, methods 
for calculating those metrics vary among simulators. Some model the 
system of facilities, economics, and materials at static equillibrium, while 
others capture its dynamics.  
Similarly, while some simulators discretely model material and facilities, 
others treat materials in streams and facilities in fleets, in an aggregated 
fashion. Depending on their intended use, simulators often overspecialize, 
modeling a single aspect of the fuel cycle in great detail while neglecting 
others. A simulator created for policy modeling might have excellent 
capability in economics while material isotopics and transmutation detail are 
neglected.

@@

In addition to providing the fundamental features expected in fuel cycle 
simulators, the \Cyclus paradigm enables major capabilites that previous 
simulators lack. First, its \emph{modular and open architecture}  facilitates 
targeted contribution and collaboration within the nuclear fuel cycle analysis 
community.  Additionally, \emph{agent interchangability} facilitates direct 
comparison of modeling methodologies. Finally, the flexibility and generality 
of its \emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach} 
emphasizes applicability of the \Cyclus tool accross a broader range of 
applications than other simulators.

Modeling the evolution of a physics-dependent, international nuclear fuel supply
chain is a difficult problem. To date, it has been treated relatively
lightly. Tools have either focused on macro effects, e.g., the fleet-level
stocks and flows of commodities, or micro effects, e.g., the used fuel
composition fast reactor fuel. Accordingly, each focus has driven the
development of these tools, rendering the task of answering questions between
the macro and micro levels either impossible or difficult and time consuming.

@@

The encapsulated plug-in architecture within the \Cyclus tool allows developers 
to define nuclear fuel cycle facility processes independent of the simulation 
logic. This design choice acheives two things. First, analysts across 
institutions can take advantage of the simulation logic \gls{API} and 
archetype ecosystem when they apply \Cyclus to their specific problem. The effort they 
undertake can thereby be focused on creating or customizing 
nuclear facility, institution, resource, and toolkit models within their 
specific area of expertise.

% we could use a specific example of Cosi's equivalence method below
Second, because \Cyclus uses a modular archetype approach, comparing two 
archetypes is straightforward. Consider a case in which an analyst would like 
to compare the effect of using different models to determining input fuel 
composition for fast reactors. A variety fuel fabrication archetypes can be 
developed and used interchangably to analyze the effect of each on a 
simulation's output.

@@

This generality specifically permits the use cases that cannot be acheived with 
fleet-based models. That is, some questions require resolution at the level of 
individual facilities and individual materials.  Since fleet-based, 
lumped-material models do not distinguish between discrete facility entities or 
discrete materials, many detailed performance metrics cannot be captured with 
those tools.

One example use case seeks to capture system vulnerability to nefarious 
material diversion. This type of analysis requires discrete simulation of a 
target facility and the individual materials modified within it and is only 
acheivable with discretely-modeled objects like those in the \Cyclus simulator.

>>>>

Historically, nuclear fuel cycle simulators have estimated 
nuclear fuel cycle performance using software 
ranging from ad hoc spreadsheet-driven flow calculators to highly specialized 
proprietary models. To date, current tools are either static, fleet-based, 
privately distributed, or all of the above. Each of these qualities present a 
severe challenge to modeling fidelity, generality, efficiency, robustness, and 
scientific transparency.

@@

% Common goals of fuel cycle simulation/simulators (driving &d focus,
% approximating tech. impacts, etc.)
% Previous work (cite all the tools!)
% Limitations of previous simulators by others (fleet-based, closed
% development, inflexible infrastructure)
% Previous attempts by this group (GENIUS v1/v2)
% note NGFCS

@@

This cycle has resulted in a proliferation of specialized
fuel cycle simulators for the calculation of fuel cycle metrics.  Accordingly, methods 
for calculating those metrics vary among simulators. Some model the 
system of facilities, economics, and materials at static equilibrium, while 
others capture its dynamics.  
Similarly, while some simulators discretely model material and facilities, 
others treat materials in streams and facilities in fleets, in an aggregated 
fashion. Depending on their intended use, simulators often overspecialize, 
modeling a single aspect of the fuel cycle in great detail while neglecting 
others. A simulator created for policy modeling might have excellent 
capability in economics while material isotopics and transmutation detail are 
neglected.

@@

In addition to providing the fundamental features expected in fuel cycle 
simulators, the \Cyclus paradigm enables major capabilities that previous 
simulators lack. First, its \emph{modular and open architecture}  facilitates 
targeted contribution and collaboration within the nuclear fuel cycle analysis 
community.  Additionally, \emph{agent interchangeability} facilitates direct 
comparison of modeling methodologies. Finally, the flexibility and generality 
of its \emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach} 
emphasizes applicability of the \Cyclus tool across a broader range of 
applications than other simulators.

Modeling the evolution of a physics-dependent, international nuclear fuel supply
chain is a multiscale problem. Tools have either focused on macro effects, e.g., the fleet-level
stocks and flows of commodities, or micro effects, e.g., the used fuel
composition fast reactor fuel. Accordingly, each focus has driven the
development of these tools, rendering the task of answering questions between
the macro and micro levels either impossible or difficult and time consuming.

@@

The encapsulated plug-in architecture within the \Cyclus tool allows developers 
to define nuclear fuel cycle facility processes independent of the simulation 
logic. This design choice achieves two things. First, analysts across 
institutions can take advantage of the simulation logic \gls{API} and 
archetype ecosystem when they apply \Cyclus to their specific problem. The effort they 
undertake can thereby be focused on creating or customizing 
nuclear facility, institution, resource, and toolkit models within their 
specific area of expertise.

% we could use a specific example of Cosi's equivalence method below
Second, because \Cyclus uses a modular archetype approach, comparing two 
archetypes is straightforward. Consider a case in which an analyst would like 
to compare the effect of using different models to determining input fuel 
composition for fast reactors. A variety fuel fabrication archetypes can be 
developed and used interchangeably to analyze the effect of each on a 
simulation's output.

@@

This generality specifically permits the use cases that cannot be achieved with 
fleet-based models. That is, some questions require resolution at the level of 
individual facilities and individual materials.  Since fleet-based, 
lumped-material models do not distinguish between discrete facility entities or 
discrete materials, many detailed performance metrics cannot be captured with 
those tools.

One example use case seeks to capture system vulnerability to nefarious 
material diversion. This type of analysis requires discrete simulation of a 
target facility and the individual materials modified within it and is only 
achievable with discretely-modeled objects like those in the \Cyclus simulator.
